Homicide Increases in the COVID-19 Era

### 2025-03-06 Draft3.qmd
Updated draft

# Regression Analyses

@@

@@

## Chi-Square for Zip Code

```{r}
homicides_by_zip <- homicides %>% group_by(ZCTA5CE20) %>% summarize(HomicideCount = n()) %>% ungroup()
chisq.test(x = as.character(homicides_by_zip$ZCTA5CE20), y = homicides_by_zip$HomicideCount)
```

@@

crime_zctas$LON <- as.numeric(gsub('c(', "", crime_zctas$LON, fixed = TRUE))
crime_zctas$LAT <- as.numeric(gsub(')', "", crime_zctas$LAT, fixed = TRUE))
```

>>>>

# Statistical Analyses

To examine the relationship between the number of homicides and various socioeconomic and enforcement factors, we will use a variety of statistical analyses to see if certain factors are more influential in causing increases or decreases in homicide rates.

For the purposes of this analysis, homicide rate is quantified as the annual number of homicides in a particular entity, whether that is ZIP Code Tabulation Area (ZCTA) or Census Tract. Additionally, we will examine the influence of general geographic location through the latitude and longitude where the homicide was committed.

@@

### Discussion

@@

## Negative Binomial for Census Block

```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(kableExtra)
crimes_by_cb <- read.csv("0_Data/Cleaned_Data/crimes_by_census_block.csv")
colnames(crimes_by_cb) <- c(colnames(crimes_by_cb)[-c(1, length(colnames(crimes_by_cb)))],"LON", "LAT")

crimes_by_cb$LON <- as.numeric(gsub('c(', "", crimes_by_cb$LON, fixed = TRUE))
crimes_by_cb$LAT <- as.numeric(gsub(')', "", crimes_by_cb$LAT, fixed = TRUE))

crimes_by_cb$DateParsed <- as.POSIXct(crimes_by_cb$Date.Rptd, 
                                  format = "%m/%d/%Y %I:%M:%S %p", 
                                  tz = "America/Los_Angeles")

crimes_by_cb$YearWeek <- format(crimes_by_cb$DateParsed, "%Y-%U")

crimes_by_cb$year <- as.integer(stringr::str_sub(crimes_by_cb$YearWeek, 1, 4))

homicides_by_cb <- crimes_by_cb %>% filter(Crm.Cd.Desc == "CRIMINAL HOMICIDE") %>% group_by(BLKGRPCE, year) %>% summarize(HomicideCount = n()) %>% ungroup()

# shapiro.test(homicides_by_cb$HomicideCount) # cannot use parametric tests. Strong evidence against normality.

mean_homicides <- mean(homicides_by_cb$HomicideCount)
var_homicides <- var(homicides_by_cb$HomicideCount)
# since variance > mean, use negative binomial 
library(MASS)
model <- glm.nb(HomicideCount ~ as.factor(BLKGRPCE), data = homicides_by_cb)

summary(model)
```
### Discussion

@@

crime_zctas$LON <- as.numeric(gsub('c(', "", crime_zctas$LON, fixed = TRUE))
crime_zctas$LAT <- as.numeric(gsub(')', "", crime_zctas$LAT, fixed = TRUE))

# Repeat same process for Census Blocks
```
